---
title: "STA426 Exercise 1.B"
author: "KCervaG"
date: "9/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###  Instructions

1. _Create an HTML document that samples 100 values from a log-normal distribution (say, mu=1, sigma=.25)._ 

2. _Create a histogram of the distribution and the distribution on the log scale 
report the mean and variance of the sample in line in the text._


**The following sample was created through the function rlnorm to obtain log-normal distributed values, mean, sd and variance.**

#### _Rcode to generate random samples from a normal distribution_
```{r rlnorm}
rlnorm <- rlnorm(100, 1, 0.25)
rlnorm
mean (rlnorm)
sd (rlnorm)
var(rlnorm)
```



#### Sample characteristics

The log-normal distributed sample randomly generated has a mean of 2.855466, a standard deviation of 0.6585066 and a variance of 0.433631.



#### Sample distribution visualization

Here, the hist function was used to generate  histograms of the distribution and log distribution of the rlnorm sample. plot function was used to visualize the 100 samples generated.

```{r histogram}
hist (rlnorm)
hist(log(rlnorm))
plot(rlnorm, type='h')
plot(rlnorm, log = "y", type = 'h')
```

